PeerMind

### 2016-08-12 paper.tex

\begin{displaymath}
\mathbf{v} = \left[ \begin{array}{c}
0.70 \\
0 \\
-0.4 \\
0 \\
0 \\
\end{array} \right],\quad \mathbf{x_v} = \left[ \begin{array}{c}
0.70 \\
0.54 \\
-0.40 \\
0.056 \\
0 \\
\end{array} \right]
\end{displaymath}

There are few details we have to look into.
Despite delegation some votes or parts of votes can still happen to be discarded.
Members who did not vote might have not declared their delegates.
Other members could delegate to them as well, potentially propagating lack of a vote further.
In our example, member $M_4$ has not voted so their vote is discarded.
As a consequence $M_3$'s vote cannot be computed fully, which influences $M_1$'s vote as well.

>>>>

\begin{displaymath}
\mathbf{v} = \left[ \begin{array}{c}
0.70 \\
0 \\
-0.4 \\
0 \\
0 \\
\end{array} \right],\quad \mathbf{x_v} = \left[ \begin{array}{c}
0.70 \\
0.54 \\
-0.40 \\
0.056 \\
0 \\
\end{array} \right]
\end{displaymath}
\todo[inline]{Max: FYI, computing who to discard from the population as ``non-voting'' is a separate computation in itself.  You need to figure out what votes can be calculated partially as a consequence of delegation, and which cannot.  Use indicator vectors denoting 1 if member has voted, else 0.}
There are few details we have to look into.
Despite delegation some votes or parts of votes can still happen to be discarded.
Members who did not vote might have not declared their delegates.
Other members could delegate to them as well, potentially propagating lack of a vote further.
In our example, member $M_4$ has not voted so their vote is discarded.
As a consequence $M_3$'s vote cannot be computed fully, which influences $M_1$'s vote as well.
